---
title: "New Rmarkdown Doc"
author: "Eric Ellison"
date: "2024-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 5

Going to save the file and stage it.
By doing this, have to click on the __Git__ tab in the environment and tick the __Staged__ box under the document. 

## Question 6

Create a new commit including the new file and push it to github (check on github that it works)

## Question 7

Edit the file. Delete everything after line 12. Add a new section title, simplet text and text in bold font. Then knit and compile.

I already did that so just gonna add another section title, simple textk, and text in bold then knit and compile. 

### New section title

Some simple text and __some text in bold__

## Question 8

Make a new commit (with a meaningful message), and push to github.

Meaningful Message: "_Would you rather be feared or loved? Easy, both. I want people to be afraid of how much they love me_" - Micheal Scott

## Question 9

Create a new branch, and add a new section to the rmarkdown file in this branch. Whatever you want. I would suggest a graph of the data. 

### New Section

I'm gonna make a graph of the data
```{r}
library(palmerpenguins)
head(penguins)
```


